formula1

### 2020-04-01 inst/formula1.Rmd
idiom

L2017 <- hyper2(pnames=alldrivers) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
        suppressWarnings(o <- as.numeric(levels(o))[o])
        o[is.na(o)] <- 0
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	L2017 <- order_obs(L2017,o)
}  # for(i) loop closes
head(L2017)
```

>>>>

L2017 <- hyper2(pnames=alldrivers) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
        suppressWarnings(o <- as.numeric(levels(o))[o])
        o[is.na(o)] <- 0
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	L2017 %<>% order_obs(o)
}  # for(i) loop closes
head(L2017)
```
